---
title: "**tidflo: An R package for drawing 'flowy' data and plots**"
author: "**Dalton Leibold and D.W.A. Noble**"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    toc-title: "**Table of Contents**"
    output-file: "index.html"
    theme: simplex
    embed-resources: true
    code-fold: show
    code-tools: true
    number-sections: true
    fontsize: "12"
    max-width: "10"
    code-overflow: wrap
crossref: 
  fig-title: Figure     # (default is "Figure")
  tbl-title: Table     # (default is "Table")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Tab.    # (default is "Table")
editor_options: 
  chunk_output_type: console
---


```{r setup}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE)
options(digits=2)
```


# **Citing `tidyflo`**

To cite `tidyflo` in publications one can use the following reference:

Shinichi Nakagawa, Malgorzata Lagisz, Rose E. O'Dea, Patrice Pottier, Joanna Rutkowska, Alistair M. Senior, Yefeng Yang, Daniel W.A. Noble. 2023. orchaRd 2.0: An R package for visualizing meta-analyses with orchard plots. **Methods in Ecology and Evolution**, https://doi.org/10.1111/2041-210X.14152 (preprint = **EcoEvoRxiv**, https://doi.org/10.32942/X2QC7). 

# **Installation**

To install `orchaRd` use the following code in R:


:::{.column-margin}
:::{.callout-note}
If you want to download the development branch, which contains newer features you can execute the following code:

```{r loadtidyflo_dev}
#| label: loadtidyflo_dev
#| echo: true
#| eval: false
#| results: hide
#| code-fold: true
rm(list = ls())
pacman::p_load(devtools, tidyverse, patchwork, flextable)
devtools::install_github("daltonleibold/tidyflo", ref = "dev", force = TRUE)
pacman::p_load(tidyflo)
```

It's important to note that this version may not be as stable as the master branch.

:::
:::

```{r loadtidyflo}
#| label: loadtidyflo
#| echo: true
#| results: hide
#| code-fold: true
#| eval: false
#| warning: FALSE
#| message: FALSE

#install.packages("pacman")
rm(list = ls())
pacman::p_load(devtools, tidyverse, patchwork, flextable)
devtools::install_github("daltonleibold/tidyflo", ref = "main", force = TRUE)
pacman::p_load(tidyflo)
```

Installation will make the primary functions accessible to users along with their help files. You will also need the `tidyverse` and `metafor` packages.